PCA Toolkit

### 2019-10-22 pca-toolkit.Rmd
best
save

Perform PCA analyses in iPSYCH appropriately and quickly.

@@

- Perform pruning to reduce effect of Linkage Disequilibrium (LD)

@@

Method: Robust Mahalanobis distances by reference population.

```{r, out.width="70%"}
knitr::include_graphics("figures/us.svg")
```

>>>>

Perform PCA analyses in iPSYCH quickly and following best practices.

@@

- Perform pruning or clumping to reduce effect of Linkage Disequilibrium (LD)

@@

Method: Robust Mahalanobis distance for each reference population    
\+ minimum distance (or maximum p-value).

```{r, out.width="65%"}
knitr::include_graphics("figures/us.svg")
```
